Proposed Solution

### 2016-11-11 Ennan-Proposal/related.tex
config: f

Language support has been considered a promising way  
to tackle configuration problems~\cite{xu15systems}.
Nevertheless, a practical language-based misconfiguration
detection approach still remains an open problem.

>>>>

Verification support to configuration files 
has been considered a promising way  
to tackle misconfiguration problems~\cite{xu15systems}.
Nevertheless, a practical misconfiguration
verification approach still remains an open problem.
